Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels

### 2018-05-22 articles/formalism/sections/real_space_formalism.tex
Added some reference and some detail to kernel paintbrush section.

\paragraph{Radiating kernel.} The expression we call the \textit{radiating kernel}  allows us, like a Green's function, to evaluate the $E/B$ field contribution due to a single Stoke parameter ``charge'' at a fixed location. The total $E/B$ maps can then be thought of as the superposed radiation emerging from Stokes charges across the sphere. In this picture, we are effectively in the frame of the Stokes charge ${}_{\pm2}X$ and evaluate its contribution to the complex spin-0 scalar field $E+iB$ across the sphere.

The $E$/$B$ contribution from the Stokes parameters at some location $\hat{n}_q$ is given by the following expression (\eq{eq:op_qu2eb_rad} and \eq{eq:qu2eb_op}),
%
\beq  \label{eq:qu2eb_radiation_explicit}
\bar{S}_q(\hat n_e) = \bmat E_e \\ B_e  \emat_{q} =- {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{q e}) & \sin(2\alpha_{q e})\\  -\sin(2 \alpha_{q e})  & \cos(2 \alpha_{q e}) \emat  \bmat Q_{q} \\ U_{q}  \emat \Delta \Omega \,.
\eeq
%
The total map can be simply evaluated by summing over the contribution from the Stokes parameters at each location $\hat{n}_q$: $\bar{S} = \sum_{q=1}^{N_{\rm pix}} \bar{S}_q$. This operation can be cast concisely as,
%
\begin{subequations} \label{eq:qu2eb_radiation_concise}
\beqry 
\left[E + iB\right](\hat{n}_e) &=& -\Delta \Omega  \sum_{q=1}^{N_{\rm pix}} \Big[ {}_{+2}X(\hat{n}_{q}) e^{-i2\alpha_{q e}} \Big]  {{}_{\mm}f}(\beta_{q e}) \,, \\
%&=&    \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {}_{+2}X(\hat{n}_{q}) \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2}(\beta_{qe},\alpha_{qe}) \right] \Bigg\rbrace \,, \\
&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \,  \mathcal{M}_{G}(\hat n_e,\hat{n}_q) \,,
\eeqry
\end{subequations}
%
where the last line is a simple scalar multiplication between complex numbers.  The radiating kernel is then:
\beq
 \mathcal{M}_{G}(\hat{n}_e,\hat n_q) =  - \Delta \Omega {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) e^{-i2\alpha_{q e}}
\eeq
%. $\mathcal{M}_{G}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\alpha_{qe}$ and it
is $-\Delta\Omega \mm^*$ and can be thought of as the Green's function of the operator.  That is, $[E +iB](\hat n_e) = \mathcal{M}_{G}(\hat n_e,\hat n_q)$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU](\hat n) = [\delta(\hat{n}-\hat{n}_q) + i0]$. We display the kernel later in \fig{fig:vis_kernel}.

>>>>

\paragraph{Radiation kernel.} The expression we call the \textit{radiation kernel}  allows us, like a Green's function, to evaluate the $E/B$ field contribution due to a single Stoke parameter ``charge'' at a fixed location. The total $E/B$ maps can then be thought of as the superposed radiation emerging from Stokes charges across the sphere. In this picture, we are effectively in the frame of the Stokes charge ${}_{\pm2}X$ and evaluate its contribution to the complex spin-0 scalar field $E+iB$ across the sphere.

The $E$/$B$ contribution from the Stokes parameters at some location $\hat{n}_q$ is given by the following expression (\eq{eq:op_qu2eb_rad} and \eq{eq:qu2eb_op}),
%
\beq  \label{eq:qu2eb_radiation_explicit}
\bar{S}_q(\hat n_e) = \bmat E_e \\ B_e  \emat_{q} =- {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{q e}) & \sin(2\alpha_{q e})\\  -\sin(2 \alpha_{q e})  & \cos(2 \alpha_{q e}) \emat  \bmat Q_{q} \\ U_{q}  \emat \Delta \Omega \,.
\eeq
%
The total map can be simply evaluated by summing over the contribution from the Stokes parameters at each location $\hat{n}_q$: $\bar{S} = \sum_{q=1}^{N_{\rm pix}} \bar{S}_q$. This operation can be cast concisely as,
%
\begin{subequations} \label{eq:qu2eb_radiation_concise}
\beqry 
\left[E + iB\right](\hat{n}_e) &=& -\Delta \Omega  \sum_{q=1}^{N_{\rm pix}} \Big[ {}_{+2}X(\hat{n}_{q}) e^{-i2\alpha_{q e}} \Big]  {{}_{\mm}f}(\beta_{q e}) \,, \\
%&=&    \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {}_{+2}X(\hat{n}_{q}) \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y^*_{\ell 2}(\beta_{qe},\alpha_{qe}) \right] \Bigg\rbrace \,, \\
&=& \sum_{q=1}^{N_{\rm pix}} {}_{+2}X(\hat{n}_{q}) \,  \mathcal{M}_{G}(\hat n_e,\hat{n}_q) \,,
\eeqry
\end{subequations}
%
where the last line is a simple scalar multiplication between complex numbers.  The radiation kernel is then:
\beq
 \mathcal{M}_{G}(\hat{n}_e,\hat n_q) =  - \Delta \Omega {{}_{\mm}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) e^{-i2\alpha_{q e}}
\eeq
%. $\mathcal{M}_{G}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\alpha_{qe}$ and it
is $-\Delta\Omega \mm^*$ and can be thought of as the Green's function of the operator.  That is, $[E +iB](\hat n_e) = \mathcal{M}_{G}(\hat n_e,\hat n_q)$ is the spin-0 scalar field generated from the delta-function Stokes field $[Q+iU](\hat n) = [\delta(\hat{n}-\hat{n}_q) + i0]$. We display the kernel later in \fig{fig:vis_kernel}.
